resevol: an R package for spatially explicit models of pesticide resistance

### 2022-07-19 notebook/ms/ms.Rmd
Write a new journal post explaining the new changes in version 0.3.1.0, and why they are useful. Add a bit more to the manuscript draft
Code Figure 2 for the manuscript draft

Individual pests can be modelled to have several reproductive systems and life histories.

>>>>

Individual pests can be modelled to have several reproductive systems and life histories.
Pest reproductive system can be specified in the `run_farm_sim` function using the `repro` argument, which accepts arguments "asexual" (haploid), "sexual" (monoecious), and "biparental" (dioecious).
For "sexual" pests, the `selfing` argument specifies if self-fertilisation is (`TRUE`) or is not (`FALSE`) allowed.
At the start of a simulation, pests are initialised in a random location.
Initialised pests are age of zero if `rand_age = FALSE` or a random age from zero to `max_age` if `rand_age = TRUE`.
Following initialisation, a single time step proceeds with landscape change (see above), pest aging, feeding, pesticide consumption, movement, reproduction, mortality, and immigration.
Feeding, pesticide consumption, movement, and reproduction all depend on pest age.
Pests feed and consume pesticide from ages `min_age_feed` to `max_age_feed`, move from ages  `min_age_move` to `max_age_move`, and reproduce from ages `min_age_reproduce` to `max_age_reproduce` (all inclusive).
Food accumulated is lost during aging if `baseline_metabolism > 0` and pest age is within `min_age_metabolism` and `max_age_metabolism`.
The option to set minimum and maximum ages for events makes it possible to model pests with much different life histories [e.g., @Sudo2018].

```{r, echo=FALSE, fig.height=3, fig.width=8, fig.cap = "Overview of simulated events in the resevol R package. Note that metabolism, feeding, pesticide consumption, movement, and reproduction are all subject to a minimum and maximum pest age. Consequently, simulation order might not reflect the order of events from the perspective of a focal pest (e.g., pests might move from ages 1-2, but only feed from ages 2-4). Crops and pesticides are also not necessarily rotated in each time step (see Landscape). Statistics collected within a time step are printed in a CSV file."}
mbox <- function(x0, x1, y0, y1){
    xx <- seq(from=x0, to=x1, length.out = 100);
    yy <- seq(from=y0, to=y1, length.out = 100);
    xd <- c(rep(x0, 100), xx, rep(x1,100), rev(xx));
    yd <- c(yy, rep(y1,100), rev(yy), rep(y0, 100));
    return(list(x=xd, y=yd));
}
par(mar=c(0,0,0,0));
# ===============================================================
plot(x=0, y=0, type="n", xlim=c(0,100), ylim=c(40,95), xaxt="n", yaxt="n",
     xlab="",ylab="");
ibox <- mbox(x0 = 0,  x1 = 10, y0 = 63, y1 = 47);
polygon(x = ibox$x, y = ibox$y, lwd = 5, border = "black", col = "white");
cbox <- mbox(x0 = 0, x1 = 10, y0 = 88, y1 = 72);
polygon(x = cbox$x, y = cbox$y, lwd = 3, border = "black", col = "white");
ubox <- mbox(x0 = 15, x1 = 25, y0 = 88, y1 = 72);
polygon(x = ubox$x, y = ubox$y, lwd = 3, border = "black", col = "white");
nbox <- mbox(x0 = 30, x1 = 40, y0 = 88, y1 = 72);
polygon(x = nbox$x, y = nbox$y, lwd = 3, border = "black", col = "white");
fbox <- mbox(x0 = 45, x1 = 55, y0 = 88, y1 = 72);
polygon(x = fbox$x, y = fbox$y, lwd = 3, border = "black", col = "white");
tbox <- mbox(x0 = 60, x1 = 70, y0 = 88, y1 = 72);
polygon(x = tbox$x, y = tbox$y, lwd = 3, border = "black", col = "white");
tbox <- mbox(x0 = 75, x1 = 85, y0 = 88, y1 = 72);
polygon(x = tbox$x, y = tbox$y, lwd = 3, border = "black", col = "white");
tbox <- mbox(x0 = 90, x1 = 100, y0 = 88, y1 = 72);
polygon(x = tbox$x, y = tbox$y, lwd = 3, border = "black", col = "white");
ibox <- mbox(x0 = 90,  x1 = 100, y0 = 63, y1 = 47);
polygon(x = ibox$x, y = ibox$y, lwd = 3, border = "black", col = "white");
tbox <- mbox(x0 = 75, x1 = 85, y0 = 63, y1 = 47);
polygon(x = tbox$x, y = tbox$y, lwd = 3, border = "black", col = "white");
text(x=5,  y=58, labels="Initialise", col="black", cex = 0.75);
text(x=5,  y=54, labels="pests and", col="black", cex = 0.75);
text(x=5,  y=50, labels="landscape", col="black", cex = 0.75);
text(x=5, y=84, labels="Crops and", col="black", cex = 0.75);
text(x=5, y=80, labels="pesticides", col="black", cex = 0.75);
text(x=5, y=76, labels="rotated?", col="black", cex = 0.75);
text(x=20, y=82, labels="Pests", col="black", cex = 0.75);
text(x=20, y=78, labels="metabolise", col="black", cex = 0.75);
text(x=35, y=82, labels="Pests", col="black", cex = 0.75);
text(x=35, y=78, labels="feed", col="black", cex = 0.75);
text(x=50, y=82, labels="Pesticide", col="black", cex = 0.75);
text(x=50, y=78, labels="consumed", col="black", cex = 0.75);
text(x=65, y=82, labels="Pests", col="black", cex = 0.75);
text(x=65, y=78, labels="move", col="black", cex = 0.75);
text(x=80, y=82, labels="Pests", col="black", cex = 0.75);
text(x=80, y=78, labels="reproduce", col="black", cex = 0.75);
text(x=95, y=82, labels="Pest", col="black", cex = 0.75);
text(x=95, y=78, labels="mortality", col="black", cex = 0.75);
text(x=95,  y=58, labels="Pests", col="black", cex = 0.75);
text(x=95,  y=54, labels="immigrate", col="black", cex = 0.75);
text(x=80,  y=59, labels="Collect", col="black", cex = 0.75);
text(x=80,  y=55, labels="statistics", col="black", cex = 0.75);
text(x=80,  y=51, labels="as CSV", col="black", cex = 0.75);
arrows(x0=2, x1=2,   y0=63, y1=71.5, lwd=2, length=0.10);
arrows(x0=10, x1=14.5, y0=80, y1=80, lwd=2, length=0.10);
arrows(x0=25, x1=29.5, y0=80, y1=80, lwd=2, length=0.10);
arrows(x0=40, x1=44.5, y0=80, y1=80, lwd=2, length=0.10);
arrows(x0=55, x1=59.5, y0=80, y1=80, lwd=2, length=0.10);
arrows(x0=70, x1=74.5, y0=80, y1=80, lwd=2, length=0.10);
arrows(x0=85, x1=89.5, y0=80, y1=80, lwd=2, length=0.10);
arrows(x0=95, x1=95,   y0=72, y1=63.5, lwd=2, length=0.10);
arrows(x0=90, x1=85.5, y0=55, y1=55, lwd=2, length=0.10);
arrows(x0=75, x1=70.5, y0=60, y1=60, lwd=2, length=0.10);
arrows(x0=60, x1=55.5, y0=60, y1=60, lwd=2, length=0.10);
rbox <- mbox(x0 = 60, x1 = 70, y0 = 57, y1 = 63);
polygon(x = rbox$x, y = rbox$y, lwd = 3, border = "black", col = "black");
text(x=65, y=60, labels="Extinction?", col="white", cex = 0.75);
rbox <- mbox(x0 = 45, x1 = 55, y0 = 57, y1 = 63);
polygon(x = rbox$x, y = rbox$y, lwd = 3, border = "black", col = "black");
text(x=50, y=60, labels="Max. time?", col="white", cex = 0.75);
text(x = 58.5, y = 58.5, labels = "No", col = "black", cex = 0.75);
text(x = 43.5, y = 58.5, labels = "No", col = "black", cex = 0.75);
text(x = 68, y = 54, labels = "Yes", col = "black", cex = 0.75);
text(x = 53, y = 54, labels = "Yes", col = "black", cex = 0.75);
arrows(x0=66, x1=66, y0=57, y1=50, lwd=2, length=0.0);
arrows(x0=51, x1=51, y0=57, y1=50, lwd=2, length=0.0);
rbox <- mbox(x0 = 30, x1 = 40, y0 = 47, y1 = 53);
polygon(x = rbox$x, y = rbox$y, lwd = 3, border = "black", col = "black");
text(x=35, y=50, labels="STOP", col="white", cex = 1);
rbox <- mbox(x0 = 10, x1 = 16, y0 = 47, y1 = 63);
polygon(x = rbox$x, y = rbox$y, lwd = 5, border = "black", col = "black");
text(x=13, y=55, labels="START", col="white", cex = 1, srt = 90);
arrows(x0=66, x1=40.5, y0=50, y1=50, lwd=2, length=0.10);
arrows(x0=45, x1=35, y0=60, y1=60, lwd=2, length=0.0);
arrows(x0=35, x1=35, y0=60, y1=67, lwd=2, length=0.0);
arrows(x0=35, x1=7, y0=67, y1=67, lwd=2, length=0.0);
arrows(x0=7, x1=7, y0=67, y1=71.5, lwd=2, length=0.1);
```

Pests feed by

Pesticide is consumed during feeding

Movement is modelled by

Pests reproduce by

Immigration occurs.
